Ants-Review: A Protocol For Open Anonymous Peer-Reviews

### 2020-07-25 paper-v1.tex
blockchain for science (inverted order), removed redundant paragraph in design section

Besides a growing number of applications ranging from business, healthcare, music industry, government, identity to cite but a few, blockchain technology has recently started to catalyse the attention of the scientific community as well \cite{Bitcoin-Nature-focus,vanRossum2017-DigSci} with the promising potential of being a 'game changer' in outdated and broken scientific practices and leading towards Open Science \cite{AES}. In particular, a 'blockchainified science'\cite{BlockchainforScience} could 'reduce waste'\cite{ReducingWaste-Lancet}, by disclosing each step the research cycle to 'scientific self-correction' way before the final publication step and therefore help fixing the current reproducibility crisis in science. Finally, scholars have pointed out how the intrinsic characteristics of blockchain technology (decentralization, for which there are no trusted third parties; cryptographic hashing and timestamping, that create a digital footprint able to keep a traceable chronological record of research objects; immutability or append-only, for which data cannot be altered or retrieved) set the basis for a open science infrastructure \cite{ReviewBlockchain2019} where decisional processes are transparent and therefore more democratically accessible to all the stakeholders (researchers, reviewers, funders, taxpayers).

@@

\paragraph{Transparency and re-usability of the records.} The peer-review history, including authors' replies and editors' recommendations, should be openly and permanently accessible to the community ('open report' of open peer-reviews) even before articles' publication in order to  make editorial decisions more democratic and prevent waste of knowledge. Following the example of models offered by journals peer-review consortia, such as the Neuroscience Peer Review Consortium \cite{NeuroPeerCons} and independent companies like ResearchSquare \cite{ResSqu} and Peerage of Science \cite{Peerage}, peer-reviews in Ants-Review will be transferable ('cascading' or 'portable peer-reviews').

@@

There are two possible scenarios depending if Ants-Review integrates an existing journal or if Ants-Review becomes a platform completely decoupled from journals.

\begin{enumerate}
    \item \textbf{Ants-Review process - scenario 1 (journal-dependent)}: The author submits a manuscript to the journal. If the papers passes the stages of editorial decision (appropriateness of style and coherence with the journal's scope). The editor issues a bounty (\emph{bounty issuance}) for the paper review. Fulfillment rules are set in a smart-contract. The bounty prize could correspond to part of the article submission fees and article publication fees requested to the authors by the journal. Reviews fulfilling the smart-contract requirements are validated by the journal editors and voted via QV. When the reviews are accepted (\emph{bounty fulfillment}), reviewers are awarded a token called \emph{ANTS}.
    \item \textbf{Ants-Review process - scenario 2 (community-driven)}: The author submits a manuscript to the pre-print service or to an hypothetical Ants-Review platform. The paper is accepted by the community for revision in its whatever format. The author issues a bounty (\emph{bounty issuance}) for the paper review. Fulfillment rules are set in a smart-contract. The bounty prize could come by a community stake that participates in the peer-review process either as a reviewer or as a reviewer checker. Reviews fulfilling the smart-contract requirements are validated by the Ants-Review community of contributors. When the reviews are accepted (\emph{bounty fulfillment}), reviewers awarded a token called \emph{ANTS}. Reviews will be voted by the community via Quadratic Voting.In order to incentive 'fair play' also the review checkers who vote for the best quality reviews will share the final prize from the bounty. Since it is in their own interest to 'bet' on a good review, this gamed system will discourage internal dynamics prompt to favour specific members of the community beyond real personal merit and therefore will fuel ethical behaviour.

\end{enumerate}

>>>>

Besides a growing number of applications ranging from business, healthcare, music industry, government, identity to cite but a few, blockchain technology has recently started to catalyse the attention of the scientific community as well \cite{Bitcoin-Nature-focus,vanRossum2017-DigSci} with the promising potential of being a 'game changer' in outdated and broken scientific practices and leading towards Open Science \cite{AES}. Indeed, scholars have pointed out how the intrinsic characteristics of blockchain technology set the basis for a open science infrastructure \cite{ReviewBlockchain2019} where decisional processes are transparent and therefore more democratically accessible to all the stakeholders (researchers, reviewers, funders, taxpayers). Those are: \emph{decentralization}, for which there are no trusted third parties; \emph{cryptographic hashing} and \emph{timestamping}, that create a digital footprint able to keep a traceable chronological record of research objects; \emph{immutability} or \emph{append-only}, for which data cannot be altered or retrieved. In particular, a 'blockchainified science'\cite{BlockchainforScience} could 'reduce waste'\cite{ReducingWaste-Lancet}, by disclosing each step the research cycle to 'scientific self-correction' way before the final publication step and therefore help fixing the current reproducibility crisis in science.

@@

\paragraph{Transparency and re-usability of the records.} The peer-review history, including authors' replies and editors' recommendations, should be openly and permanently accessible to the community (in the form of 'open reports' of open peer-reviews) even before articles' publication in order to  make editorial decisions more democratic and prevent waste of knowledge. Following the example of models offered by journals peer-review consortia, such as the Neuroscience Peer Review Consortium \cite{NeuroPeerCons} and independent companies like ResearchSquare \cite{ResSqu} and Peerage of Science \cite{Peerage}, peer-reviews in Ants-Review will be transferable across journals (like in 'cascading' or 'portable peer-reviews').

@@
